WIDS 2024 Final Project

### 2024-01-09 Code/R FIle.qmd
fixed typo

```{r}
map_data <- full_state_data |> 
  select(c("year", "state", "state_abbreviation", "party_state_avaerage")) |> 
  distinct(year, state, .keep_all = TRUE) |> 
  filter(year %% 4==0) |> 
  filter(!is.na(party_state_avaerage))

>>>>

```{r}
map_data <- full_state_data |> 
  select(c("year", "state", "state_abbreviation", "party_state_average")) |> 
  distinct(year, state, .keep_all = TRUE) |> 
  filter(year %% 4==0) |> 
  filter(!is.na(party_state_avaerage))
